Tree level scattering amplitude in (De)constructed gauge theory

### 2025-04-19 Intermediate report/main.tex
New

    If we consider the meromorphic function $\frac{\hat{A}_n(z)}{z}$ in the complex plane, pick a contour that surrounds the simple pole at the origin. 
    \textcolor{red}{$\bigstar$ The most important point here is that}
    \begin{equation*}
        \boxed{\color{red}\mathrm{Res}|_{z=0}\frac{\hat{A}_n(z)}{z}=\hat{A}_n(0)=A_n}
    \end{equation*}
    It means that the original amplitude equals to the residue at origin.
\end{frame}
\begin{frame}
    From Cauchy Theorem, we can ontain
    \begin{equation*}
        A_n=-\sum_{z_I}\textrm{Res}|_{z=z_I}\frac{\hat{A}_n(z)}{z}+B_n,
    \end{equation*}
    where $B_n$ is the residue of the pole at $z=\infty$, called boundary term.
    \vspace{-1em}
    \begin{figure}[htbp]
        \centering
        \includegraphics[width=0.3\textwidth]{CT.png}
    \end{figure}
    \vspace{-1.5em}
    %Then, at a $z_I$ pole, the propagator $\hat{P}_I^2$ goes to on-shell. In that limit, the shifted amplitude
    %\textcolor{red}{factorizes} into to on-shell parts (Unitarity)
    \begin{equation*}
        \hat{A}_n(z)\quad \xrightarrow{z\,\text{near}\,z_I} \quad \hat{A}_L(z_I)\frac{1}{\hat{P}_I^2}\hat{A}_R(z_I)= - \frac{z_I}{z-z_I}\hat{A}_L(z_I)\frac{1}{P_I^2}\hat{A}_R(z_I)
    \end{equation*}
    This makes it easy to evaluate the residue at $z=z_I$
    \begin{equation*}
        -\mathrm{Res}|_{z=z_I}\frac{\hat{A}_n(z)}{z}=\hat{A}_L(z_I)\frac{1}{P_I^2}\hat{A}_R(z_I)
    \end{equation*}
\end{frame}

@@

    \renewcommand{\arraystretch}{1.3}
    \setlength{\tabcolsep}{6pt}
    \begin{tabular}{|c|c|c|c|}
        \hline
        \textbf{3-point} & \textbf{4-point} & \textbf{5-point} & \textbf{6-point} \\
        \hline
        $\bm{V_1\Phi\Phi^\dagger}$ & $\bm{V_1V_1V_1V_1}$ & $\bm{V_1V_1V_1V_1V_1}$ & $\bm{V_1V_1V_1V_1V_1V_1}$ \\
        $\bm{V_2\Phi\Phi^\dagger}$ & $\bm{V_2V_2V_2V_2}$ & $\bm{V_2V_2V_2V_2V_2}$ & $\bm{V_2V_2V_2V_2V_2V_2}$ \\
        $\bm{V_1V_1V_1}$ & $\bm{\Phi^\dagger V_1V_1\Phi}$ & $\bm{\Phi^\dagger V_1V_1V_1\Phi}$ & $\bm{\Phi^\dagger V_1V_1V_1V_1\Phi}$ \\
        $\bm{V_2V_2V_2}$ & $\bm{\Phi V_2V_2\Phi^\dagger}$ & $\bm{\Phi V_2V_2V_2\Phi^\dagger}$ & $\bm{\Phi V_2V_2V_2V_2\Phi^\dagger}$ \\
        & $\bm{\Phi V_2 \Phi^\dagger V_1}$ & $\bm{V_2\Phi^\dagger V_1V_1\Phi}$ & $\bm{V_2V_2\Phi^\dagger V_1V_1\Phi}$ \\
        & $\bm{\Phi\Phi^\dagger\Phi\Phi^\dagger}$ & $\bm{\Phi V_2V_2\Phi^\dagger V_1}$ & $\bm{\Phi V_2V_2\Phi^\dagger V_1V_1}$ \\
        & & \textcolor{red}{$\Phi\Phi^\dagger\Phi\Phi^\dagger V_1$} & $\vdots$ \\
        & & \textcolor{red}{$\Phi\Phi^\dagger\Phi\Phi^\dagger V_2$} & $\vdots$ \\
        \hline
    \end{tabular}
\end{frame}
\begin{frame}
    \frametitle{Basic building block -- 3-point}
    From the previous section, we have known that there are only two kinds of 3 point amplitude
    \begin{gather*}
        A[1,2,3^+]=\frac{[23][31]}{[12]},\qquad A[1,2,3^-]=\frac{\avg{23}\!\avg{31}}{\avg{12}}\\
        A[3^+,4^+,5^-]=\frac{[34]^3}{[45][53]},\qquad A[3^-,4^-,5^+]=\frac{\avg{34}^3}{\avg{45}\!\avg{53}}
    \end{gather*}
    By using the 3 point building block, we can construct 4 point color-ordered amplitudes from BCFW recursion relation.
\end{frame}
\begin{frame}
    \frametitle{Gauge boson sector}
    \begin{itemize}
        \item n$ V_1$ or n$V_2$\\
        This part is completely the same as the pure gluon amplitude, so we can directly borrow the
        existing results.
        \begin{equation*}
            \boxed{\text{Parke - Talyor Formula}:\quad A[\cdots,i^-,\cdots,j^-,\cdots]=\frac{\avg{ij}^4}{\avg{12}\!\avg{23}\cdots\avg{n1}}}
        \end{equation*}
        \textcolor{red}{Notice that this formula only applies for MHV amplitudes, although the NMHV can be completely solved.}
    \end{itemize}
\end{frame}

@@

\begin{frame}
    \frametitle{Pure 2-site amplitude}
    \begin{itemize}
        \item $\Phi V_2 \Phi^\dagger V_1$
        \begin{equation*}
            A[1,2,3_1^+,4_2^-]=\frac{\mdavg{14}{24}}{\mdavg{13}{23}}
        \end{equation*}
        \item $\Phi V_2 \Phi^\dagger V_1V_1$
        \begin{equation*}
            A[1,2,3_1^+,4_1^+,5_2^-]=(-1)\frac{\avg{2\textcolor{green}{5}}^2\!\avg{1\textcolor{green}{5}}^2}{\textcolor{blue}{\mdavg{23}{34}\!\avg{41}}\textcolor{red}{\mdavg{25}{51}}}
        \end{equation*}
        \item $\Phi V_2V_2 \Phi^\dagger V_1V_1$
        \begin{equation*}
            A[1,2,3_1^+,4_1^+,5_2^+,6_2^-]=\frac{\avg{2\textcolor{green}{6}}^2\!\avg{1\textcolor{green}{6}}^2}{\textcolor{blue}{\mdavg{23}{34}\!\avg{41}}\!\textcolor{red}{\mdavg{25}{56}\!\avg{51}}}
        \end{equation*}       
    \end{itemize}
\end{frame}

@@

    \end{itemize}
\end{frame}
\section{Summary and Outlook}
\begin{frame}
    \frametitle{Summary}
    \begin{itemize}
        \item Introduce the on-shell method, including BCFW recursion relation, color-ordered amplitudes. etc.
        \item Introduce a (de)constructed gauge theory model, which is an effective field theory for 5 dimension gauge theory.
        \item The locality plays an important role to relate the spacetime locality and field space locality.
        \item Much of the scattering amplitudes in this model can be recursively computed by BCFW, and some compact formulas can be obtained.
    \end{itemize}
\end{frame}
\begin{frame}
    \frametitle{Possible future work}

>>>>

    If we consider the meromorphic function $\frac{\hat{A}_n(z)}{z}$ in the complex plane, pick a contour that surrounds the single pole at the origin. 
    \textcolor{red}{$\bigstar$ The most important point here is that}
    \begin{equation*}
        \boxed{\color{red}\mathrm{Res}|_{z=0}\frac{\hat{A}_n(z)}{z}=\hat{A}_n(0)=A_n}
    \end{equation*}
    It means that the original amplitude equals to the residue at origin.
\end{frame}
\begin{frame}
    From Cauchy Theorem, we can ontain
    \begin{equation*}
        A_n=-\sum_{z_I}\textrm{Res}|_{z=z_I}\frac{\hat{A}_n(z)}{z}+B_n,
    \end{equation*}
    where $B_n$ is the residue of the pole at $z=\infty$, called boundary term.
    \vspace{-1em}
    \begin{figure}[htbp]
        \centering
        \includegraphics[width=0.3\textwidth]{CT.png}
    \end{figure}
    \vspace{-1.5em}
    %Then, at a $z_I$ pole, the propagator $\hat{P}_I^2$ goes to on-shell. In that limit, the shifted amplitude
    %\textcolor{red}{factorizes} into to on-shell parts (Unitarity)
    \begin{equation*}
        \hat{A}_n(z)\quad \xrightarrow{z\,\text{near}\,z_I} \quad \hat{A}_L(z_I)\frac{1}{\hat{P}_I^2}\hat{A}_R(z_I)= - \frac{z_I}{z-z_I}\hat{A}_L(z_I)\frac{1}{P_I^2}\hat{A}_R(z_I)
    \end{equation*}
    This makes it easy to evaluate the residue at $z=z_I$
    \begin{equation*}
        -\mathrm{Res}|_{z=z_I}\frac{\hat{A}_n(z)}{z}=\hat{A}_L(z_I)\frac{1}{P_I^2}\hat{A}_R(z_I)
    \end{equation*}
\end{frame}

@@

    \renewcommand{\arraystretch}{1.3}
    \setlength{\tabcolsep}{6pt}
    \begin{tabular}{|c|c|c|c|}
        \hline
        \textbf{3-point} & \textbf{4-point} & \textbf{5-point} & \textbf{6-point} \\
        \hline
        $\bm{V_1\Phi\Phi^\dagger}$ & $\bm{V_1V_1V_1V_1}$ & $\bm{V_1V_1V_1V_1V_1}$ & $\bm{V_1V_1V_1V_1V_1V_1}$ \\
        $\bm{V_2\Phi\Phi^\dagger}$ & $\bm{V_2V_2V_2V_2}$ & $\bm{V_2V_2V_2V_2V_2}$ & $\bm{V_2V_2V_2V_2V_2V_2}$ \\
        $\bm{V_1V_1V_1}$ & $\bm{\Phi^\dagger V_1V_1\Phi}$ & $\bm{\Phi^\dagger V_1V_1V_1\Phi}$ & $\bm{\Phi^\dagger V_1V_1V_1V_1\Phi}$ \\
        $\bm{V_2V_2V_2}$ & $\bm{\Phi V_2V_2\Phi^\dagger}$ & $\bm{\Phi V_2V_2V_2\Phi^\dagger}$ & $\bm{\Phi V_2V_2V_2V_2\Phi^\dagger}$ \\
        & $\bm{\Phi V_2 \Phi^\dagger V_1}$ & $\bm{V_2\Phi^\dagger V_1V_1\Phi}$ & $\bm{V_2V_2\Phi^\dagger V_1V_1\Phi}$ \\
        & $\bm{\Phi\Phi^\dagger\Phi\Phi^\dagger}$ & $\bm{\Phi V_2V_2\Phi^\dagger V_1}$ & $\bm{\Phi V_2V_2\Phi^\dagger V_1V_1}$ \\
        & & \textcolor{red}{$\Phi\Phi^\dagger\Phi\Phi^\dagger V_1$} & $\vdots$ \\
        & & \textcolor{red}{$\Phi\Phi^\dagger\Phi\Phi^\dagger V_2$} & $\vdots$ \\
        \hline
    \end{tabular}
\end{frame}
\begin{frame}
    \frametitle{Basic building block -- 3-point}
    From the previous section, we have known that there are only two kinds of 3 point amplitude
    \begin{gather*}
        A[1,2,3^+]=\frac{[23][31]}{[12]},\qquad A[1,2,3^-]=\frac{\avg{23}\!\avg{31}}{\avg{12}}\\
        A[3^+,4^+,5^-]=\frac{[34]^3}{[45][53]},\qquad A[3^-,4^-,5^+]=\frac{\avg{34}^3}{\avg{45}\!\avg{53}}
    \end{gather*}
    By using the 3 point building block, we can construct 4 point color-ordered amplitudes from BCFW recursion relation.
\end{frame}
\begin{frame}
    \frametitle{Gauge boson sector}
    \begin{itemize}
        \item n$ V_1$ or n$V_2$\\
        This part is completely the same as the pure gluon amplitude, so we can directly borrow the
        existing results.
        \begin{equation*}
            \boxed{\text{Parke - Talyor Formula}:\quad A[\cdots,i^-,\cdots,j^-,\cdots]=\frac{\avg{ij}^4}{\avg{12}\!\avg{23}\cdots\avg{n1}}}
        \end{equation*}
        \textcolor{red}{Notice that this formula only applies to MHV amplitudes, although the NMHV can be completely solved.}
    \end{itemize}
\end{frame}

@@

\begin{frame}
    \frametitle{Pure 2-site amplitude}
    \begin{itemize}
        \item $\Phi V_2 \Phi^\dagger V_1$
        \begin{equation*}
            A[1,2,3_1^+,4_2^-]=\frac{\mdavg{14}{24}}{\mdavg{13}{23}}
        \end{equation*}
        \item $\Phi V_2 \Phi^\dagger V_1V_1$
        \begin{equation*}
            A[1,2,3_1^+,4_1^+,5_2^-]=(-1)\frac{\avg{2\textcolor{green}{5}}^2\!\avg{1\textcolor{green}{5}}^2}{\textcolor{blue}{\mdavg{23}{34}\!\avg{41}}\textcolor{red}{\mdavg{25}{51}}}
        \end{equation*}
        \item $\Phi V_2V_2 \Phi^\dagger V_1V_1$
        \begin{equation*}
            A[1,2,3_1^+,4_1^+,5_2^+,6_2^-]=\frac{\avg{2\textcolor{green}{6}}^2\!\avg{1\textcolor{green}{6}}^2}{\textcolor{blue}{\mdavg{23}{34}\!\avg{41}}\!\textcolor{red}{\mdavg{25}{56}\!\avg{61}}}
        \end{equation*}       
    \end{itemize}
\end{frame}

@@

    \end{itemize}
\end{frame}
\section{Summary and Outlook}
\begin{frame}
    \frametitle{Summary}
    \begin{itemize}
        \item Introduce the on-shell method, including BCFW recursion relation, color-ordered amplitudes. etc.
        \item Introduce a (de)constructed gauge theory model, which is an effective field theory for 5 dimension gauge theory.
        \item The locality plays an important role to relate the spacetime locality and field space locality.
        \item Much of the scattering amplitudes in this model can be recursively computed by BCFW, and some compact formulas are offered.
    \end{itemize}
\end{frame}
\begin{frame}
    \frametitle{Possible future work}
